---
title: "Trial work for A1"
author: "Akshay Kapoor & Rishi Shah"
date: "31/01/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


``` {r, explore, echo = FALSE}
#?ChickWeight
```
# Looking what data we have
A help seacrch on this dataset in R returns the following summary of data :

The **chickWeight** data is a built in data "Weight versus age of chicks on different diets", this dataframe has 578 rows and 4 columns from an experiment on the effect of diet on early growth of chicks.

It includes the following data-features : 
**weight**: a numeric vector giving the body weight of the chick (gm).
**Time**: a numeric vector giving the number of days since birth when the measurement was made.
**Chick**: an ordered factor with levels 18 < ... < 48 giving a unique identifier for the chick. The ordering of the levels groups chicks on the same diet together and orders them according to their final weight (lightest to heaviest) within diet.
Diet: a factor with levels 1,2,3, 4 indicating which experimental diet the chick received.

Lets look at the few samples from the data set
``` {r, see_the_data, echo =TRUE}
chicken_dataset <-ChickWeight
df_temp<-chicken_dataset[sample(nrow( chicken_dataset), 5),]
rownames(df_temp)<-NULL
print(df_temp)
#chicken_dataset
```
By looking at the above data, we can see we have chicken weight for various time/days(vary from day=0 to day =21), and this data is for various chick which are labelled (from 1 to 50) and are kept on different diets (diets vary in group of chicks and are labelled as 1,2,3 and 4).

Lets dive deep into each parameter data we collected for our experiment :

1. weight
its a numerical- ratio variable, and is an important feature of the dataset.
lets see the distribution of weight for the given data.

``` {r, mean_weight, echo = FALSE}
dataset_weight<-chicken_dataset$weight
mean_weight<-mean(dataset_weight)
range_weight<- range(dataset_weight)
sd_weight<- sd(dataset_weight)
median_weight <- median(dataset_weight)

```

The weight has following distribution parameters,
mean : `r mean_weight`, range: (`r range_weight`), standard_deviation :`r sd_weight`, median : `r median_weight`.

Lets see the distribution for the the weight among all the data points:
``` {r, plot1}
library(tidyverse)
weights <- chicken_dataset %>% 
  group_by(weight) %>% 
  summarise(weight_count = n())
#weights
ggplot(data=weights, aes(x = weight, y =weight_count)) +
  geom_col()

```
``` {r}
ggplot(data=chicken_dataset, aes(x = weight, fill = "red")) +
  geom_density()+ xlim(-5,450)
```

By looking at data we can see, the weight distribution is right skewed, which means there is asymmertry in data, which can be because of following :
1. Different diets affect the weight in diffrent way and there non- uniform distribution of number of chicken for each diet.
2. Data for some chicks is not taken for all of the days.


2. Lets have a look at **Time**
Here Time, is a numerical ratio variable, measured in number of days.
It represents number of days from the birth of the chicken.

``` {r,}
chicken_time <- chicken_dataset$Time
summary(chicken_time)

```


By looking at the above plot we can see, at day = 0 we started with 50 Chicks and had data for all of chicken weights, as we moved on the number of data for various Chicks decreased, at the end of day =21 we just had access to the data for 45 chicks.
Also, we can see the median of Time is still at 10 days, which means there is data is not very un-symmertric, we had access to 48 Chicks weight data at day =10.

3. Lets look at  **chicks** column of our dataset 
Chicks column represent the labels used to identify the chickens kept under obsevation, it is stored as ordinal data
ranging from 1 to 50.

``` {r,echo = FALSE, include = FALSE}
chicks<-chicken_dataset$Chick
chicks
```


``` {r,}
chicks<-chicken_dataset$Chick
ggplot(chicken_dataset, aes (x = Chick, y= Time)) + geom_col() 
```

By looking at the Time vs Chick column of the dataset we can see, there are 50 chickens and we have data from day = 0 to day = 21 for most of chickens, 
except for Chick number =18, 16,15,8and 44


4. Lets look at The Diets parameter
Its a nominal parameter, which varies as numerical values as 1,2,3,4.
Lets see the count plot for each type of Diet :

```
So, we have four types of Diet, lets see the distribution of various diets
``` {r,}
library(ggplot2)
ggplot(data = chicken_dataset, aes(x=Diet, fill= Diet))+geom_bar()
```
we can see see, we have more data for diet=1 (220 entries) and less data for diet= 2(120 entries),3(120 entries),4(118 entries).We have almost equal data for Diet =2,3and 4.

======================================================================================================================================================
Lets start analyzing the data now :


``` {r,}
data_diet1 <- filter(ChickWeight,Diet==1)
data_diet2 <- filter(ChickWeight,Diet==2)
data_diet3 <- filter(ChickWeight,Diet==3)
data_diet4 <- filter(ChickWeight,Diet==4)

(dim(data_diet1))
(dim(data_diet2))
(dim(data_diet3))
(dim(data_diet4))


```

# Analysis

Lets dive into analysis mode, lets see how data varies.
It is time to see the growth of weight of chickens for various diets 

``` {r,}
g = ggplot(data = ChickWeight,  aes(x = weight, fill = Diet))
g + geom_density(alpha = 0.5) + xlim(0,400) + facet_grid(rows =vars(Diet))
```

Lets Plot the data of diet for day = 0 and day = 20

``` {r,}
library("Rmisc")
data_diet1_day20 <- filter(ChickWeight,Time ==20)
data_diet2_day20 <- filter(ChickWeight,Time ==20)
data_diet3_day20 <- filter(ChickWeight,Time ==20)
data_diet4_day20 <- filter(ChickWeight,Time ==20)

CI_diet1_day_20 <- CI(data_diet1_day20$weight, .95)
CI_diet2_day_20 <- CI(data_diet2_day20$weight, .95)
CI_diet3_day_20 <- CI(data_diet3_day20$weight, .95)
CI_diet4_day_20 <- CI(data_diet4_day20$weight, .95)
```

```{r,}
data_day0 <- filter(ChickWeight, Time==0)
```

``` {r,}
ggplot(data = data_day0, aes(y = weight, x = Diet, fill =Diet)) + geom_boxplot()
```
``` {r,}
ggplot(data = data_day0, aes(y = weight, x = Diet)) + geom_col()
```

``` {r,}
ggplot(data = data_day20, aes(y = weight, x = Diet, fill = Diet)) + geom_boxplot()+theme_bw()
```

``` {r,}
ggplot(data = data_day20, aes(y = weight, x = Diet)) + geom_col()
```

lets see how weight increases with number of days for various diets
``` {r,}
ggplot(chicken_dataset, aes(x= Time, y = weight, color = Diet))+ geom_point() + geom_smooth(se = FALSE)+ theme_bw()

```
``` {r,}
ggplot(data = data_day20, aes(x = weight,fill = Diet)) + geom_density()+theme_bw()+ facet_wrap(~Diet)
```

``` {r,}
library("Rmisc")
```
``` {r}
data_21 <- summarise_at(group_by(data_day20, Diet), vars(weight),funs(mean(weight)))
data_21
```
``` {r}

quantiles_95 <- function(x)
{
  p <- quantile(x,probs = c (0.05,0.25,0.5,0.75,0.95))
  names (p) <- c ("ymin","lower","middle","upper","ymax")
  p
}

quantiles_95(data_day20$weight)
ggplot(data = data_day20, aes (y = weight, x = Diet, fill = Diet))+ guides(Fill=F) + coord_flip() + stat_summary(fun.data= quantiles_95, geom = "boxplot")

```

``` {r,}
ggplot(data = data_day0, aes (y = weight, x = Diet, fill = Diet))+ guides(Fill=F) + coord_flip() + stat_summary(fun.data= quantiles_95, geom = "boxplot")
```

``` {r,}
ggplot(data = chicken_dataset, aes (y = weight, x = Time), color = Diet)+ geom_col()
```

